It's easier to move sideways

### 2023-09-07 manuscript.Rmd
updated arms table and fixed image link

![An Autonomous reef monitoring structure (ARMS) unit deployed on a reef in the Red Sea (photo credit: Michael Berumen, used with permission)](data/images/berumen_uncropped.png){#fig:fig_arms}

@@

```{r arms-table,results="asis", dependson="init"}
arms_schedule <- cc$crabs_untransformed %>%
  sample_tibble() %>%
  separate_wider_regex(sample,patterns=c(recovery_year="^[0-9]+","_",sample=".*"))  %>%
  select(sample,everything()) %>%
  unite("range",deployment_year,recovery_year,sep="--") %>%
  mutate(
    island = case_when(
      str_remove_all(hawaiian_name,'[^a-zA-Z ]') != island ~ as.character(str_glue("{hawaiian_name} ({island})")),
      TRUE ~ as.character(hawaiian_name)
    ),
    island = fct_reorder(island,-lat)
  ) %>%
  count(island,range) %>%
  pivot_wider(names_from="range",values_from="n")  %>%
  select(island,order(colnames(.))) %>%
  mutate(across(-island,~replace_na(.x,0)))
print_table(arms_schedule,"arms_table","ARMS unit sampling schedule (number of units)") 
```

>>>>

![An autonomous reef monitoring structure (ARMS) unit deployed on a reef in the Red Sea (photo credit: Michael Berumen, used with permission)](data/images/arms_example.png){#fig:fig_arms}

@@

```{r arms-table,results="asis", dependson="init"}
arms_schedule <- cc$crabs_untransformed %>%
  sample_tibble() %>%
  separate_wider_regex(sample,patterns=c(recovery_year="^[0-9]+","_",sample=".*"))  %>%
  select(sample,everything()) %>%
  unite("range",deployment_year,recovery_year,sep="--") %>%
  mutate(
    island = case_when(
      str_remove_all(hawaiian_name,'[^a-zA-Z ]') != island ~ as.character(str_glue("{hawaiian_name} ({island})")),
      TRUE ~ as.character(hawaiian_name)
    ),
    island = case_when(
      island == "O‘ahu" ~ str_glue("{hawaiian_name} ({shallow_deep})"),
      TRUE ~ island
    ),
    island = fct_reorder(island,-lat)
  ) %>%
  count(island,range) %>%
  pivot_wider(names_from="range",values_from="n")  %>%
  select(island,order(colnames(.))) %>%
  mutate(across(-island,~replace_na(.x,0)))
print_table(arms_schedule,"arms_table","ARMS unit sampling schedule (number of units)") 
```
